---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
  html_document:
    self_contained: false
    toc: true
    toc_float: false
---

```{r rsetup,eval=TRUE,include=FALSE}
require(codecheck)
require(knitr)
require(rprojroot)
require(yaml)
require(xtable)
require(tibble)
require(readr)
options(width=60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r rsetup-knitr, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}
manifest_df = copy_manifest_files(root, manifest,
                                  dest_dir, keep_full_path=FALSE)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
xt = xtable(manifest_df[, c("output", "comment", "size")],
            digits=0,
            caption="Summary of output files generated")
print(xt, include.rownames=FALSE, comment=FALSE)
```

# Summary

The check was successful, without larger issues.
The runtime environment was not specified at all but could be derived.
The created graphs match the ones provided by the authors.
However, these figures not perfectly resemble the ones from the original paper.

# How to cite this report

```
Daniel Nüst. (2020, May 14). CODECHECK certificate 2020-004. Zenodo.
http://doi.org/10.5281/zenodo.3827371
```

\clearpage

# CODECHECKER notes

The github repo  contained all the necessary code.
The test code was written in Python and there was a `Makefile`.
I did not take a look at the C code at all.

I used a virtual environment to run the Python code, using Python 3 because of the sheband in `main.py`.
I created `codecheck/requirements.txt` with trial and error to identify the required libraries.

Run the following code in a command line, then render this document (see `codecheck/Makefile`).
The rendering copies the generated files to the CODECHECK directory.

```bash
#mkvirtualenv --python=$(which python3) barto-sutton-anderson-1983

cd python\ code
mv output/ output.backup
mkdir output

make

cd ../codecheck/
make clean codecheck.pdf
```

This took about 6 minutes on my laptop computer (8 cores, 40GB RAM).

Note that `python code/Makefile` does only mention one output file, but the script actually generates both.

\clearpage

```{r, echo=FALSE, fig.cap=manifest_df[1:7,"comment"]}
knitr::include_graphics(manifest_df[1, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[2, "dest"])
```

\clearpage
# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the file.

```{r}
sessionInfo()
```
